\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

I would like to extend my heartfelt gratitude to my project supervisor, Prof. Roberto Galeazzi. His profound insights and guidance have opened my eyes to the fascinating world of Unmanned Aerial Vehicles (UAVs) and the intricacies of project management. His patience and constant encouragement have been instrumental in fueling my continuous learning journey in this field, molding me into a more skilled engineer. His flexible approach to project development, coupled with a stringent attitude towards process management, has significantly enhanced my understanding of effective project execution.

I am also immensely grateful to Ph.D Peter Iwer Hoedt Karstensen for his consistent guidance and invaluable assistance with the experimental aspects of my thesis. His anecdotes and positive energy, especially during our regular weekly meetings, have been a source of inspiration. Moreover, his anecdotes about life in Finland, from the massive snowfalls to the long winter nights, brought much-needed levity and energy to my tight project schedule, helping to alleviate stress.

My sincere thanks also go to the many individuals involved in the broader aspects of my project, whose lively and fruitful discussions have contributed greatly to my learning experience. Their advice and insights, though they were not officially part of my thesis, have been incredibly valuable.

My journey would have been significantly less joyful without the support of my friends and my girlfriend, whose companionship has been a pillar of strength. The laughter, talks, and shared experiences have not only kept me grounded but also provided much-needed moments of levity and relaxation amidst the rigors of academic life.

Lastly, I owe an immeasurable debt of gratitude to my family in China. Their relentless support and love over the past two years have been the bedrock of my ability to embark on this journey at DTU and start this remarkable chapter of my life. Their sacrifices have not gone unnoticed and have been the wind beneath my wings, allowing me to soar to new heights.